Data Specialization for a Staged Lambda Calculus

### 2015-02-25 paper/paper.tex
wrote a new intro to splitting section
expanded figures
minor
a little work on examples and implementation
culling some old intro text
related work
title
small edits all over
a bit more work

\lstset{%language=ML,
        columns=fullflexible,
        keepspaces=true,
        basicstyle=\ttfamily,
        tabsize=4,
%        escapeinside={"*}{*"},
        escapeinside={@}{@},
        moredelim=*[is][\color{stageOneColor}]{1`}{`},
        moredelim=*[is][\color{stageTwoColor}]{2`}{`},
        moredelim=*[is][\color{stageMonoColor}]{3`}{`},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {murec}{{$\mu$}}1
                 {alpha}{{$\alpha$}}1
                 {beta}{{$\beta$}}1
                 {atsign}{{@}}1
                 {^}{{$\curr$}}1
                 {$}{{$\fut$}}1}

@@

\title{Data Specialization for a Staged Lambda Calculus}

@@

\section{Intro}

(placeholder in order to keep section numbers stable)

In \ref{fig:termSplitSummary}, we summarize the terminology of our
formal development.

%% \input{intro}

\input{example}
\input{semantics}

%% %\vfill\eject\pagebreak
\input{splitting}
\input{implementation}
\input{algoexamples}
\input{relatedwork}
\input{umut}

@@

>>>>

\lstset{%language=ML,
        columns=fullflexible,
        keepspaces=true,
        basicstyle=\ttfamily,
        tabsize=4,
%        escapeinside={"*}{*"},
        escapeinside={@}{@},
        moredelim=*[is][\color{stageOneColor}]{1`}{`},
        moredelim=*[is][\color{stageTwoColor}]{2`}{`},
        moredelim=*[is][\color{stageMonoColor}]{3`}{`},
        literate={|->}{{\ $\mapsto$\ }}1
                 {xhat}{{$\hat{\texttt{x}}$}}1
                 {yhat}{{$\hat{\texttt{y}}$}}1
                 {zhat}{{$\hat{\texttt{z}}$}}1
                 {murec}{{$\mu$}}1
                 {alpha}{{$\alpha$}}1
                 {beta}{{$\beta$}}1
                 {atsign}{{@}}1
                 {literalone}{1}1 % hax
                 {literaltwo}{2}1 % hax
                 {^}{{$\curr$}}1
                 {$}{{$\fut$}}1}

@@

%% Vote on your favorite title! Lower is better!
\title{Data Specialization for a Staged Lambda Calculus}
\title{Algorithmically Staged Lambda Calculus}
\title{Algorithmic Staging}
\title{Automatically Splitting a Staged Lambda Calculus}

@@

\input{intro}

\input{example}

\input{semantics}

\input{splitting}

\input{implementation}

\input{algoexamples}
\input{relatedwork}
%\input{umut}

@@

%% %\vfill\eject\pagebreak
